Appendix to 'Detecting social information in a dense database of infants’ natural

### 2021-05-25 paper/preprint/paper_revised_submission_april2021_apa.Rmd
fix minor typos

We also used these detailed pose annotations to explore finer-grained changes in how children experience the faces and hands of their caregivers over development. We found that the faces, hands, and people in the infant view tended to become smaller and that faces tended to be farther away and in more variable horizontal positions.  Overall, these data support the idea that the social information in view changes across development as infants become increasingly mobile an independent. As children can navigate the world on their own, they may experience fewer close-up interactions with the caregivers and more bouts of play where they are exploring the objects and things in the environment around them.

>>>>

We also used these detailed pose annotations to explore finer-grained changes in how children experience the faces and hands of their caregivers over development. We found that the faces, hands, and people in the infant view tended to become smaller and that faces tended to be farther away and in more variable horizontal positions.  Overall, these data support the idea that the social information in view changes across development as infants become increasingly mobile and independent. As children can navigate the world on their own, they may experience fewer close-up interactions with the caregivers and more bouts of play where they are exploring the objects and things in the environment around them.
